---
title: "Untitled"
date: "2024-07-17"
output: 
  powerpoint_presentation:
    reference_doc: LMN_template_V2.pptx

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with text
Hello this is my presentation

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure1}
plot(pressure)
```


## Slide with 2 columns

:::::: {.columns}
::: {.column width="50%"}
This is an explanation of the figure on the right
:::

::: {.column width="50%"}
```{r pressure_2}
plot(pressure)
```
:::
::::::




